% Autogenerated translation of outline.md by Texpad
% To stop this file being overwritten during the typeset process, please move or remove this header

\documentclass[a4paper, 12pt]{book}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage[a4paper]{geometry}
\usepackage{hyperref}
\pagestyle{plain}
\begin{document}

\chapter*{On the Performance of String Search Algorithms for Deep Packet Inspection}

\section*{Introduction}

\begin{itemize}
\item State the problem
\item Define terms like packet, rule, algorithm.
\item Talk about the modern way of performing deep packet inspection (literature review).
\item Create a hypothesis. Estimate which algorithms would perform better (maybe not based on the algorithms themselves but the on some performance indicators).
\end{itemize}

\section*{String Search Algorithms}

\begin{itemize}
\item Talk about multithreading the algorithms.
\item Speak briefly about each of the string search algorithms.
\item Speak about their pros and cons as well as their complexities.
\end{itemize}

\section*{Results}

\begin{itemize}
\item Talk about the experiment; its setup and execution.
\item Present the data here.
\item Talk about the dataset.
\end{itemize}

\section*{Analysis}

\begin{itemize}
\item Show pretty graphs and make observations about each.
\item Answer the following questions:

\begin{itemize}
\item Overall, how fast are each of the algorithms?
\item Which algorithms perform better with a large amount of data (some book text) and which with a small amount (a single packet)?
\item Which algorithms had largely fluctuating processing times? This is related to the standard deviation.
\end{itemize}
\end{itemize}

\section*{Conclusion}

\begin{itemize}
\item Talk about which algorithms performed better over and why. Recommend some.
\end{itemize}

\section*{References}

\end{document}
